Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-02-03 R0V0.tex
Change from exploiting sparsity to utilizing separable structure
Change case in which u=0 and delta_u=0 to autonomous case

\mypara The constraint on the components of $k^\ast$ described in Problem~\ref{problem formulation} is particularly relevant for the design of distributed feedback laws with a prescribed topology (described possibly by $\mathscr{G}_c$). Consider the network composed of systems described by the following equation.
\begin{equation}\label{eq:example}
	\scalebox{0.95}{$\left\{\begin{array}{rcl}
		\dot{x}_i&=&-x_i-x_i^3+y_i^2 + 0.01\left(x_{i-1}^3 - 2x_i^3 +x_{i+1}^3\right)\\
		\dot{y}_i&=&u_i\;.
	\end{array}\right.$}
\end{equation}
As explained in Section \ref{sec:Illustration}, when more than five of these systems are connected, the CCM approach was unable to provide unconstrained controller on a standard desktop machine, due to memory constraints. However, by exploring sparsity, up to 512 of theses systems can be connected and the distributed controller can be computed.

@@

\mypara The existence a contraction metric for system \eqref{eq:general system} implies that every two solutions to this system converge to each other exponentially. The proof of this claim, for the case in which $u\equiv0$ and $\delta_u\equiv0$, can be found in \cite[Theorem 1]{Lewis1951}, and \cite[Theorems 5.7 and 5.33]{Reich2005}, and \cite[Lemma 3.3]{Isac2008}.

>>>>

\mypara The constraint on the components of $k^\ast$ described in Problem~\ref{problem formulation} is particularly relevant for the design of distributed feedback laws with a prescribed topology (described possibly by $\mathscr{G}_c$). Consider the network composed of systems described by the following equation.
\begin{equation}\label{eq:example}
	\scalebox{0.95}{$\left\{\begin{array}{rcl}
		\dot{x}_i&=&-x_i-x_i^3+y_i^2 + 0.01\left(x_{i-1}^3 - 2x_i^3 +x_{i+1}^3\right)\\
		\dot{y}_i&=&u_i\;.
	\end{array}\right.$}
\end{equation}
As explained in Section \ref{sec:Illustration}, when more than five of these systems are connected, the CCM approach was unable to provide unconstrained controller on a standard desktop machine, due to memory constraints. However, by utilizing a separable structure (see definition below), up to 512 of theses systems can be connected and the distributed controller can be computed.

@@

\mypara The existence a contraction metric for system \eqref{eq:general system} implies that every two solutions to this system converge to each other exponentially. The proof of this claim, for the autonomous case, can be found in \cite[Theorem 1]{Lewis1951}, and \cite[Theorems 5.7 and 5.33]{Reich2005}, and \cite[Lemma 3.3]{Isac2008}.
